Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-09-23 main_new.tex
Updates from Overleaf

\begin{abstract}
  Improving and optimizing oceanographic sampling is a crucial task for
  modern marine management and science faced with limited resources to
  understand highly dynamic processes in the water-column. The
  combination of statistics and autonomous
  robotics provides opportunities for studying aspects related to
  experimental design for effective characterization of oceanographic
  phenomena. In this work we develop methods for efficient spatial
  sampling applied to the mapping of coastal processes by
  providing informative descriptions of spatial characteristics of ocean
  phenomena. Specifically, we define a design criterion based on
  reducing uncertainty in the joint excursions of random
  fields, and derive analytical expressions for the expected Bernoulli
  variance reduction in the excursion set of spatial temperature and
  salinity variables. We show how these can be applicable in static
  designs and sequential designs, building on myopic and look-ahead
  sampling strategies. We use simulations to study the properties and
  differences between state-of-the-art approaches. Results from field
  deployments with an autonomous underwater vehicle are also presented,
  for a case study mapping the boundary of a river plume. The results
  demonstrate the ability of the method to effectively inform and
  execute data-driven environmental sampling.

@@

Traditional data collection at sea has typically been based on static
buoys, lagrangian floats or ship-based methods, with significant
logistical limitations that directly impact coverage and sampling
resolution. Modern methods using satellite remote-sensing provide
large-scale coverage, but have limited resolution, are limited to
sensing the surface of the ocean, and is impacted by cloud cover. The
advent of robust mobile robotic platforms \cite{Bellingham07} has
resulted in significant contributions to environmental monitoring and
sampling. In particular autonomous underwater vehicles (AUVs), have made
strides in advancing the state of sampling and consequently have made
robotics an integral part of ocean observation in large part by our own
work % driven by
% using statistical methods in design and data assimilation
\citep{das11b,Graham2013,Das2015,das15,fossuminformation,fossum18b}.
Others include \cite{wikle2013modern} focusing on hierarchical
statistical models, \cite{sahu2008space} which studies spatio-temporal
models for sea surface temperature and salinity data, while
\cite{mellucci2018oceanic} looks at the statistical prediction of
features using an underwater glider. Common to these approaches is the
use of information-based methods to infer environmental sampling. A few
important characteristics should be mentioned, namely:

\begin{itemize}
\item Decisions on where to sample happen sequentially, i.e.  how
  recently acquired information can be assimilated and used to improve
  statistical models and reduce uncertainty associated with where to make measurements.
\item As a priori information about the state of the ocean is very
  uncertain, there lies a substantial efficiency gain in reacting to
  information obtained from measurements taken \emph{in-situ}, this is
  usually referred to as the \emph{adaptivity gap} \citep{Krause2008phd}.
\item For such types of sampling problems, the number of choices (i.e.
  locations, trajectories, and candidate designs) makes the problem
  combinatorially large, creating a trade-off between optimization
  (finding the optimal design) and computability (arriving at a
  solution in reasonable time), which has to be considered in
  practice.
\end{itemize}{}

>>>>

\begin{abstract}
  Improving and optimizing oceanographic sampling is a crucial task for
  modern marine management and science. Faced with limited resources to
  understand highly dynamic processes in the water-column, the
  combination of statistics and autonomous
  robotics provides opportunities for studying aspects related to
  experimental design for effective characterization of oceanographic
  phenomena. In this work we develop methods for efficient spatial
  sampling applied to the mapping of coastal processes by
  providing informative descriptions of spatial characteristics of ocean
  phenomena. Specifically, we define a design criterion based on
  reducing uncertainty in the joint excursions of random
  fields, and derive analytical expressions for the expected Bernoulli
  variance reduction in the excursion set of spatial temperature and
  salinity variables. We show how these can be applicable in static
  designs and sequential designs, building on myopic and look-ahead
  sampling strategies. We use simulations to study the properties and
  differences between state-of-the-art approaches. Results from field
  deployments with an autonomous underwater vehicle are also presented,
  for a case study mapping the boundary of a river plume. The results
  demonstrate the ability of the method to effectively inform and
  execute data-driven environmental sampling.

@@

Traditional data collection at sea has typically been based on static
buoys, lagrangian float,s or ship-based methods, with significant
logistical limitations that directly impact coverage and sampling
resolution. Modern methods using satellite remote-sensing provide
large-scale coverage, but have limited resolution, are limited to
sensing the surface of the ocean, and are impacted by cloud cover. The
advent of robust mobile robotic platforms \cite{Bellingham07} has
resulted in significant contributions to environmental monitoring and
sampling. In particular, autonomous underwater vehicles (AUVs), have made
strides in advancing the state of sampling and consequently have made
robotics an integral part of ocean observation in large part by our own
work % driven by
% using statistical methods in design and data assimilation
\citep{das11b,Graham2013,Das2015,das15,fossuminformation,fossum18b}.
Others include \cite{wikle2013modern} focusing on hierarchical
statistical models, \cite{sahu2008space} which studies spatio-temporal
models for sea surface temperature and salinity data, while
\cite{mellucci2018oceanic} looks at the statistical prediction of
features using an underwater glider. Common to these approaches is the
use of information-based methods to infer environmental sampling and overcome common challenges, namely:

\begin{itemize}
\item Static sampling paths fail to capture necessary features in dynamic ocean conditions. Incontrast, these approaches make decisions about where to sample  sequentially, i.e.  
  recently acquired information can be assimilated and used to improve
  statistical models and reduce uncertainty associated with where to make measurements.
\item As a priori information about the state of the ocean is very
  uncertain, there is a substantial efficiency gain in reacting to
  information obtained from measurements taken \emph{in-situ}; this is
  usually referred to as the \emph{adaptivity gap} \citep{Krause2008phd}.
\item For such types of sampling problems, the number of choices (i.e.
  locations, trajectories, and candidate designs) makes the problem
  combinatorially large, creating a trade-off between optimization
  (finding the optimal design) and computability (arriving at a
  solution in reasonable time), which has to be considered in
  practice.
\end{itemize}{}
